### 2017-02-17 draft-md-ct.tex
Fixed a bug and removed the steel plate :-)

% ========== Pstricks
\usepackage{pst-all}

@@

\noindent
Let's put 
$\displaystyle y(t) = \int_{0}^{t} \dot{u}(s) ds = -\eta \int_{0}^{t} \nabla\ell_{s}(x(s)) ds$.
Then for a fixed $x$,
\begin{equation}
\int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x}
= \frac{\ab{y(t), x}}{\eta}
\leq \frac{R^{*}(y(t)) + R(x)}{\eta}\,.
\label{eq.using.fenchel.ineq}
\end{equation}
But noting that $x(t) = \nabla R^{*}(y(t))$, 
which means that $x(t)$ is the optimizer in the definition of $R^{*}$, then
\begin{align}
\frac{R^{*}(y(t))}{\eta}
&= \frac{\ab{y(t), x(t)} - R(x(t))}{\eta} \notag \\[1mm]
&= \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(t)} ds - \frac{R(x(t))}{\eta}\,.
\label{eq.something}
\end{align}
Consider the function $\varphi(t,x) = \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x} ds$.
The time derivative is
$\dot{\varphi}(t,x) = \ab{-\nabla\ell_{t}(x(t)), x}$.
In particular, $\dot{\varphi}(t,x(t)) = \ab{-\nabla\ell_{t}(x(t)), x(t)}$,
and integrating (note that $\varphi(0,x(0)) = 0$) we get
$$
\int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(t)} ds 
= \varphi(t,x(t)) = \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(s)} ds\,.
$$
% omar's note: this last thing needs to be fixed!

% Picture 
\psset{unit=1.4pt} \vspace{3mm} \hspace{8cm}
\pspicture(0,0)(0,0)
\pspolygon[fillcolor=gray,fillstyle=crosshatch*](0,0)(70,0) (70,50)(0,50)
\rput(35,25){\psframebox*[framearc=.3]{\parbox[c]{2.5cm}{\footnotesize\centering STEEL PLATE ON ROAD}}}
\endpspicture

% omar's note: the following to be added back when the above is fixed!
%\noindent
%Therefore continuing from \eqref{eq.using.fenchel.ineq} and \eqref{eq.something} above,
%and rearranging,
%$$
%\int_{0}^{t} \ab{\nabla\ell_{s}(x(s)), x(s)} ds - \int_{0}^{t} \ab{\nabla\ell_{s}(x(s)), x} ds
%\leq \frac{R(x) - R(x(t))}{\eta}\,.
%$$
%So using the linearization trick (see \eqref{eq.linearizing.loss} above) we get
%$$
%\int_{0}^{T} [\ell_{t}(x(t)) - \ell_{t}(x^{*})] dt
%\leq \int_{0}^{T} \ab{\nabla\ell_{t}(x(t)), x(t) - x} dt
%\leq \frac{R(x) - R(x(T))}{\eta}\,.
%$$

>>>>

% ========== Pstricks
%\usepackage{pst-all}

@@

\noindent
Let's put 
$\displaystyle y(t) = \int_{0}^{t} \dot{u}(s) ds = -\eta \int_{0}^{t} \nabla\ell_{s}(x(s)) ds$.
Then for a fixed $x$,
\begin{equation}
\int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x}
= \frac{\ab{y(t), x}}{\eta}
\leq \frac{R^{*}(y(t)) + R(x)}{\eta}\,.
\label{eq.using.fenchel.ineq}
\end{equation}
But noting that $x(t) = \nabla R^{*}(y(t))$, 
which means that $x(t)$ is the optimizer in the definition of $R^{*}$, then
\begin{align}
\frac{R^{*}(y(t))}{\eta}
&= \frac{\ab{y(t), x(t)} - R(x(t))}{\eta} \notag \\[1mm]
&= \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(t)} ds - \frac{R(x(t))}{\eta}\,.
\label{eq.something}
\end{align}
Consider the function $\varphi(t,x) = \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x} ds$.
In particular, with $x$ replaced with $x(t)$ we have
$\varphi(t,x(t)) = \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(t)} ds$.
The time derivative is
\begin{align*}
\frac{d}{dt}\varphi(t,x(t))
&= \dot{\varphi}(t,x(t)) + \frac{\partial}{\partial x} \varphi(t,x(t)) \cdot \dot{x}(t) \\
&= \ab{-\nabla\ell_{t}(x(t)), x(t)} + \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), \dot{x}(t)} ds \\
&= \ab{-\nabla\ell_{t}(x(t)), x(t)} + \frac{\ab{y(t), \dot{x}(t)}}{\eta}\,.
\end{align*}
Then with integration (note that $\varphi(0,x(0)) = 0$) we get
\begin{align*}
\int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(t)} ds 
&= \varphi(t,x(t)) \\
&= \int_{0}^{t} \frac{d}{ds} \varphi(s,x(s)) ds \\
&= \int_{0}^{t} \ab{-\nabla\ell_{s}(x(s)), x(s)} ds 
     + \frac{1}{\eta} \int_{0}^{t} \ab{y(s), \dot{x}(s)} ds\,.
\end{align*}
% omar's note: this last thing needs to be fixed!

%% Picture 
%\psset{unit=1.4pt} \vspace{3mm} \hspace{8cm}
%\pspicture(0,0)(0,0)
%\pspolygon[fillcolor=gray,fillstyle=crosshatch*](0,0)(70,0) (70,50)(0,50)
%\rput(35,25){\psframebox*[framearc=.3]{\parbox[c]{2.5cm}{\footnotesize\centering STEEL PLATE ON ROAD}}}
%\endpspicture

% omar's note: the following to be added back when the above is fixed!
\noindent
So using the linearization trick (see \eqref{eq.linearizing.loss} above),
continuing from \eqref{eq.using.fenchel.ineq} and \eqref{eq.something},
and rearranging we get
\begin{align*}
\int_{0}^{T} [\ell_{t}(x(t)) - \ell_{t}(x^{*})] dt
&\leq \int_{0}^{T} \ab{\nabla\ell_{t}(x(t)), x(t) - x} dt \\
&\leq \frac{R(x) - R(x(T))}{\eta} + \frac{1}{\eta} \int_{0}^{t} \ab{y(s), \dot{x}(s)} ds\,.
\end{align*}
